Industrial Best Practice

### 2015-03-22 ibp/ibp.tex
Description
Added first stuff for the starting section - Might have to add more
about the companies

@@

\section{Plan and Roadmap, 5p}
As mentioned in Section 2, the effects modifications to APIs have on the platform’s ecosystem are explored as being negative. However, there are no existing systematic guidelines or framework s that take the ecosystem into account for how to best modify an API. Our proposed process for creating such a framework will be can be seen in Figure \ref{fig:roadmap}. This is an initial version of the roadmap \cite{!!!roadmap}, and it is advised that it is updated during the process. The main reason for this is that it is important to adapt to changes in the market, and if new needs are identified, the strategy should be redesigned to meet them.

>>>>

As the software industry and the open source movement steadily grow, the number of publicly available APIs is increasing. APIs can improve development speed \cite{stylos2006comparing}, improve software quality \cite{stylos2006comparing} and can increase software reusability \cite{afonso2012evaluating}. There is a consensus amount literature and experts that modifications to deployed APIs can have negative impacts on the users of the API \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}. The main reason is that it will require the users to update the code using the API, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}. The most common changes to APIs occur from refactoring \cite{dig2005role} \cite{xing2006refactoring}.

The problem, put simply, is this; how can effective changes be made to deployed APIs with minimal impact upon the ecosystem in which the API is utilised?

%Highlight problem and who it's for here.
Having a stable and well designed API is vital to the success of a company or product, especially if they are built around a particular API. For example, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}. The study aimed to discover if APIs with high rates of faults affected the success of an application. The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{mcdonnell2013empirical}.

Due to the negative implications that modifications to APIs cause for users, it is important to understand why changes occur. If the most common pitfalls are known before the development of new APIs begin, these mistakes could be mitigated. Likewise, if common dangers of changes to existing APIs are fully studied and understood, informed changes can be made to lessen the affect on the users. Furthermore, industry and academia can use these lessons learned to create, or enhance existing best practices of API design.

Given that software is prevalent in our lives, it is likely that poor API design changes have affected our lives at some point. One could therefore argue that this problem is important to everyone; customers, businesses and developers.

%This needs fluffing
Our solution is to provide a set of guidelines, or framework with which to follow when making changes to APIs. The framework will prioritise business motives and needs when tackling design decisions.

Exhaustive research has found that there exists very few similar soultions similar to our own. While there are countless books related to the subject [!!!list some?], very few actually aim to address the needs of busniness and customers; they are primarily focused on the developer.

%Examples of similar products
Apiary is a popular online API design service. Apiary focuses on a collaborative approach to creating APIs, the tool offers the ability to work with between 5 and 50 contributors on a single project. The unique part of this tool is that it provides a "mock" API by which customers, developers or anyone with access can work with. This stage allows quick prototyping and testing of an API before any real coding has taken place. The tool, while useful, doesn't aim to solve the problem of handling changes to APIs but is instead a good platform to quickly prototype ideas.

Mashery provide a more business oriented approach to API development. They offer a wide variety of services with API management being one of them. Quoting their website, they:

Increase productivity through uniformity and accessibility of data
Develop better customer experiences faster, for mobile and web-based applications
Achieve real-time data exchange between platforms and applications
Enhance visibility into data consumption to optimize APIs

While mashery have a more business oriented approach, they do not offer anything resembling a framework for both business and developers to use when making API design decisions.

@@

\section{Plan and Roadmap, 5p}
As mentioned in Section 2, the effects modifications to APIs have on the platform’s ecosystem are explored as being negative. However, there are no existing systematic guidelines or frameworks that take the ecosystem into account for how to best modify an API. Our proposed process for creating such a framework can be seen in Figure \ref{fig:roadmap}. This is an initial version of the roadmap \cite{!!!roadmap}, and it is advised that it is updated during the process. The main reason for this is that it is important to adapt to changes in the market, and if new needs are identified, the strategy should be redesigned to meet them.
